Improved Cation Binding to Lipid Bilayer with Negatively Charged POPS by Effective Inclusion of Electronic Polarization

### 2019-10-28 Manuscript/manuscript.tex
Updated manuscript PDFs including also TOC graphic

Some journals require a graphical entry for the Table of Contents. 
This should be laid out ``print ready'' so that the sizing of the 
text is correct.

Inside the \texttt{tocentry} environment, the font used is Helvetica 
8\,pt, as required by \emph{Journal of the American Chemical 
Society}.

The surrounding frame is 9\,cm by 3.5\,cm, which is the maximum 
permitted for  \emph{Journal of the American Chemical Society} 
graphical table of content entries. The box will not resize if the 
content is too big: instead it will overflow the edge of the box.

This box and the associated title will always be printed on a 
separate page at the end of the document.

@@

%Electronic continuum correction (ECC) is an implicit mean-field representation of 
%the electronic polarization in classical MD simulations, 
%which has been recently applied to improve empirical models for ions and
% biomolecules containing charged groups such as proteins and lipids. 
%\cite{melcr18, Pluharova2014, martinek17, duboue2018insulin, Mason2019, Duboue2018MgZn}
%For simple ions in water, the electronic polarizability
%can be taken into account by scaling the charge with a constant factor 
%%\begin{equation}
% \mbox{$ f_q = \frac{1}{\sqrt{\epsilon_{el}}} \approx 0.75$,}
%%\end{equation}
%where  $\epsilon_{el} = 1.78$ is the high-frequency dielectric constant of electrons in water \cite{leontyev09}.

Electrostatic interactions between charges in a dielectric medium are attenuated by a factor equal to the
corresponding relative permittivity (dielectric constant). Standard non-polarizable force fields are capable to
account for the dielectric response from the orientation of molecules (low-frequency), but fail to account for the electronic (high frequency) polarization.
In most biologically relevant environments this high frequency dielectric constant is ~2 (for water the value is 1.78).
This means that for a non-polarizable force field that would strictly account only for the low-frequency dielectric response
interactions between charges in aqueous environments should be further attenuated by a factor of 1.78, which is mathematically
equivalent by scaling the charges by a factor of ~0.75 \cite{leontyev09,leontyev14}. 
This electronic continuum correction (ECC), which can be view as a mean-field continuum way for accounting for electronic polarization,
has been shown to significantly improve the description of interactions between aqueous ions and biologically relevant charged groups \cite{pluharova13,kohagen14,kohagen14b,melcr18,xie16,kroutil17,bruce18}
%[dx.doi.org/10.1021/jp402532e, dx.doi.org/10.1021/jp5005693, dx.doi.org/10.1021/jz502099g, DOI: 10.1021/acs.jpcb.7b12510, https://doi.org/10.1021/acs.jpcb.5b10755, DOI:10.1007/s00894-017-3490-x, https://doi.org/10.1063/1.5017101].
This correction is particularly important for high charge density species where it helps to remove artifacts such as excessive ion pairing in water [dx.doi.org/10.1021/jp402532e, dx.doi.org/10.1021/jp310719g]. One should, however, bear in mind that existing non-polarizable force fields have been parameterized also using experimental data, which means that they may to a certain extent include implicitly electronic polaization effects. Therefore, in such cases a charge scaling factor between 0.75 and 1 should carefully be adjusted such that electronic polarization effect are not overaccounted.    
In addition to the charge, the Lennard-Jones parameter~$\sigma$ of the ions needed to be modified 
to improve the description of hydration properties of ions with respect to scattering data in these studies 
by scaling with a factor $ 0.72 < f_\sigma \leq 1$.
The reason for the small readjustment of the ionic radii is that the original force fields were often developed such that the first peak on the experimental ion-water oxygen radial distribution function was reproduced. 
Upon charge scaling this peak typically moved to slightly larger distances and the agreement with experiment was then restored by a small decrease of the Lennard-Jones~$\sigma$ parameter.
%More detailed description of ECC and its applications are contained in references \citenum{melcr18, martinek17, Pluharova2014, leontyev09, leontyev11, leontyev14}.

%Derivation of the correct scaling factor for lipids is more complicated, because
%the partial charges depend on the methods used to derive the respective force fields.
%For example, the partial charges of overall neutral molecules may already include the effects of electronic polarizability to some extent,
%and hence, the scaling factor can be larger than the theoretically derived value for ions in water, $f_q \approx 0.75$.  
Before the ECC theory was rigorously derived, similar idea was already employed in early classical 
MD simulations of lipids and surfactants using the ad hoc scaling factor of 0.5 for atomic charges  \cite{jonsson86,egberts94, berendsen1996}. 
In our recent work, we applied the ECC to the Amber based lipid14 force field of zwitterionic POPC lipid \cite{dickson14}
by scaling the partial charges and Lennard-Jones~$\sigma$ parameters of headgroup, glycerol backbone,
and carbonyl regions \cite{melcr18}. The scaling factors were optimized to reproduce 
the calcium binding affinity to POPC lipid bilayers, evaluated using the headgroup order parameters
and the electrometer concept \cite{akutsu81,altenbach84,seelig87,catte16}, and the X-ray scattering form factor
without additional ions \cite{kucerka11}, which resulted to the scaling factor values of $f_q = 0.8$ and $f_\sigma = 0.89$  \cite{melcr18}.

>>>>

\includegraphics[height=1.4 in]{../img/TOC_graphic.pdf}

For table of contents only.

@@

Electronic continuum correction (ECC) is an implicit mean-field representation of 
the electronic polarization in classical MD simulations, 
which has been recently applied to improve empirical models for ions and
 biomolecules containing charged groups such as proteins and lipids. 
\cite{melcr18, Pluharova2014, martinek17, duboue2018insulin, Mason2019, Duboue2018MgZn}
For simple ions in water, the electronic polarizability
can be taken into account by scaling the charge with a constant factor 
%\begin{equation}
 \mbox{$ f_q = \frac{1}{\sqrt{\epsilon_{el}}} \approx 0.75$,}
%\end{equation}
where  $\epsilon_{el} = 1.78$ is the high-frequency dielectric constant of electrons in water \cite{leontyev09}.
In addition to the charge, the Lennard-Jones parameter~$\sigma$ of the ions needed to be modified 
to improve the description of hydration properties of ions with respect to scattering data in these studies 
by scaling with a factor $ 0.72 < f_\sigma \leq 1$.
The reason for the small readjustment of the ionic radii is that the original force fields were often developed such that the first peak on the experimental ion-water oxygen radial distribution function was reproduced. 
Upon charge scaling this peak typically moved to slightly larger distances and the agreement with experiment was then restored by a small decrease of the Lennard-Jones~$\sigma$ parameter.
More detailed description of ECC and its applications are contained in references \citenum{melcr18, martinek17, Pluharova2014, leontyev09, leontyev11, leontyev14}.

Derivation of the correct scaling factor for lipids is more complicated, because
the partial charges depend on the methods used to derive the respective force fields.
For example, the partial charges of overall neutral molecules may already include the effects of electronic polarizability to some extent,
and hence, the scaling factor can be larger than the theoretically derived value for ions in water, $f_q \approx 0.75$.  
Before the ECC theory was rigorously derived, similar idea was already employed in early classical 
MD simulations of lipids and surfactants using the scaling factor of 0.5 for atomic charges  \cite{jonsson86,egberts94, berendsen1996}. 
In our recent work, we applied the ECC to the Amber based lipid14 force field of zwitterionic POPC lipid \cite{dickson14}
by scaling the partial charges and Lennard-Jones~$\sigma$ parameters of headgroup, glycerol backbone,
and carbonyl regions \cite{melcr18}. The scaling factors were optimized to reproduce 
the calcium binding affinity to POPC lipid bilayers, evaluated using the headgroup order parameters
and the electrometer concept \cite{akutsu81,altenbach84,seelig87,catte16}, and the X-ray scattering form factor
without additional ions \cite{kucerka11}, which resulted to the scaling factor values of $f_q = 0.8$ and $f_\sigma = 0.89$  \cite{melcr18}.
